Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-04 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
adding citation

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming.}
\end{abstract}
%
%
%
\section{Introduction}
Scheduling is one of the most crucial problems in various industrial, transportation, or healthcare applications. 
\todo{add 1-2 citations for each application} 
These applications resulted in different definitions of scheduling problems, with Job-shop Scheduling Problem (JSP) being among the most popular ones.
In JSP, operations of given jobs must be scheduled on available machines in an optimal way wrt.\ some pre-defined criteria. The latter include, for instance, minimization of makespan, i.e., the completion time of the last job, or tardiness, i.e., the sum of delays for all jobs completed after their deadlines.

However, JSP is a NP-complete combinatorial optimization problem \cite{DBLP:journals/mor/GareyJS76,SOTSKOV1995237} for which no efficient algorithms are known. Therefore, searching for an optimal solution with modern approaches like Answer Set Programming (ASP), Mixed Integer Programming, or Constraint Programming \todo{cite at least 1 paper solving JSP with these methods} often takes too much computation time, even for small instances. Practical applications require solving JSP instances of vast scale with thousands of operations \cite{zhang2010hybrid}.
As a result, many researchers focused on the development of efficient algorithms for finding high-quality approximations of the optimal schedule, including dispatching rules and other heuristic approaches~\cite{blackstone1982state}, or stochastic optimization techniques \cite{DBLP:journals/informs/VaessensAL96,DBLP:journals/jim/CalisB15}.  
The main issue of these approaches is that they require manual parametrization for a particular scheduling problem, which is tedious and error-prone. For instance, heuristic approaches might require the development of new heuristics or their combinations. Similarly, default parameters of stochastic methods might result in a finding of mediocre schedules.    
As a result, much focus of the recent research lies on the automation of the parametrization using machine learning techniques~\cite{bengio2020machine}.

@@

\begin{enumerate}
	\item Once an operation is started, it must be completed without interruption.
	\item Each job visits a machine once.
	\item A machine cannot perform more than one operation at a time.
	\item A machine is not broken.
	\item All jobs and machines are available at time 0.
\end{enumerate}
It is hard to reach a solution close to the optimal in a reasonable time, even if the number of operations to be scheduled is low. In real-life applications, the number of operations that are to be scheduled is up to $10,000$ \cite{zhang2010hybrid}, which makes the problem more complicated. The JSP has attracted the interest of many researchers in the last decades to find effective methods to solve this problem. One of these methods is decomposition. The decomposition idea is to split the problem into sub-problems, solve them separately, and then integrate those solutions to solve the whole problem. Many decomposition strategies have been proposed for solving the JSP  \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}. However, there is no guarantee of which method is the best because the performance varies according to the problem. \\

>>>>

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming.}
\end{abstract}
%
%
%
\section{Introduction}
Scheduling is one of the most crucial problems in various industrial, transportation, or healthcare applications
%\todo{add 1-2 citations for each application}
 \cite{pezzella2008genetic,chaudhry2016research,nouiri2018effective,demirbilek2019dynamically,schoenfelder2020nurse,wang2019routing,janakbhai2021blockchain}.

These applications resulted in different definitions of scheduling problems, with Job-shop Scheduling Problem (JSP) being among the most popular ones.
In JSP, operations of given jobs must be scheduled on available machines in an optimal way wrt.\ some pre-defined criteria. The latter include, for instance, minimization of makespan, i.e., the completion time of the last job, or tardiness, i.e., the sum of delays for all jobs completed after their deadlines.

However, JSP is a NP-complete combinatorial optimization problem \cite{DBLP:journals/mor/GareyJS76,SOTSKOV1995237} for which no efficient algorithms are known. Therefore, searching for an optimal solution with modern approaches like Answer Set Programming (ASP), Mixed Integer Programming, or Constraint Programming \cite{meng2020mixed,el2020job,al2017job}
%\todo{cite at least 1 paper solving JSP with these methods} 
often takes too much computation time, even for small instances. Practical applications require solving JSP instances of vast scale with thousands of operations \cite{zhang2010hybrid}.
As a result, many researchers focused on the development of efficient algorithms for finding high-quality approximations of the optimal schedule, including dispatching rules and other heuristic approaches~\cite{blackstone1982state}, or stochastic optimization techniques \cite{DBLP:journals/informs/VaessensAL96,DBLP:journals/jim/CalisB15}.  
The main issue of these approaches is that they require manual parametrization for a particular scheduling problem, which is tedious and error-prone. For instance, heuristic approaches might require the development of new heuristics or their combinations. Similarly, default parameters of stochastic methods might result in a finding of mediocre schedules.    
As a result, much focus of the recent research lies on the automation of the parametrization using machine learning techniques~\cite{bengio2020machine}.

@@

\begin{enumerate}
	\item Once an operation starts, it must be completed without interruption.
	\item Each job visits a machine once.
	\item A machine cannot perform more than one operation at a time.
	\item A machine is not broken.
	\item All jobs and machines are available at time 0.
\end{enumerate}
It is hard to reach a solution close to the optimal in a reasonable time, even if the number of operations to be scheduled is low. In real-life applications, the number of operations that are to be scheduled is up to $10,000$ \cite{zhang2010hybrid}, which makes the problem more complicated. The JSP has attracted the interest of many researchers in the last decades to find effective methods to solve this problem. One of these methods is decomposition. The decomposition idea is to split the problem into sub-problems, solve them separately, and then integrate those solutions to solve the whole problem. Many decomposition strategies have been proposed for solving the JSP  \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}. However, there is no guarantee of which method is the best because the performance varies according to the problem. \\
